---
title: "Hi there 👋"
author: "Andrea Del Cortona"
date: "updated: `r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}

# knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  comment = "\t",
  fig.path = "",
  out.width = "100%")

source("who_am_I.R")

# generate svg for intro if not there
if(!file.exists("intro.svg")){
  
  library("asciicast")

  # cast script
  cast = asciicast::record(
    "to_cast.R",
    rows = 12
  )
  
  # export to SVG
  asciicast::write_svg(
    cast,
    "intro.svg",
    window = TRUE,
    theme = "solarized-dark"
  )

}

```



![](intro.svg){width=100%}

[![LinkedIn](https://custom-icon-badges.demolab.com/badge/LinkedIn-0A66C2?logo=linkedin-white&logoColor=fff)](https://www.linkedin.com/in/andrea-del-cortona-86a75474/)
[![GitHub](https://img.shields.io/badge/GitHub-%23121011.svg?logo=github&logoColor=white)](hhttps://github.com/19ADC99)
[![Google Scholar](https://img.shields.io/badge/Google%20Scholar-4285F4?logo=Google%20Scholar&logoColor=white)](https://scholar.google.com/citations?user=CPtcBboAAAAJ&hl=en)




## 🔧 Skills, Languages, Technologies and Tools I am experienced with

- **Drug Development**: Biomarker Discovery, Target Discovery, Translational Science, Precision Medicine
- **Biology**: Biotechnology, Molecular Biology, Biochemistry, Immunology, Genetics, Microbiology
- **Bioinformatics & Data Science**: Multi-omics integration, Population Genomics, Genome Assembly & Annotation, Comparative Transcriptomics, Phylogenomics, Proteomics, Metagenomics, Cell Deconvolution
- **Languages:** bash, Python, R
- **DevOps:** Git
- **MLOps:** MLFlow
- **Cloud:** Google Cloud (Cloud function, Cloud Run, Compute Engine)

## &#x270d; Portofolio

**💊 Drug Discovery**

- [A gentle introduction to spatial transcriptomics](https://19adc99.github.io/AD_spatial/)
- Multi-omics integration for target discovery:
    - [Molecular characterization of Kidney Carcinomas](https://19adc99.github.io/cancer_deploy/p01-01-dataset-exploration.html)
    - [Discovery of Prognostic Biomarkers in Kidney Carcinomas](https://19adc99.github.io/cancer_deploy/p02-01-features-selection.html) --> Work in Progress ...
    - [Therapeutic Target Discovery in Kidney Clear Cell Cancer] --> Coming Soon!

**🧬 Comparative Genomics**

- [Viking's Project: Farmhouse ale cultures preserve brewing’s lost yeast diversity](https://19adc99.github.io/vikingsproject/) --> Work in Progress ...
- [Development of taxonomical biomarkers for Ulva genus](https://19adc99.github.io/UlvaOmics/)
- [Trappist genome evolution](https://github.com/19ADC99/Trappist_genome_evolution) --> Coming Soon!

**🧰 Bioinformatics/Data Science Tools**

- [Characterization of tumor microenvironment with infiltR](https://github.com/19ADC99/infiltR)
- [Differential Gene Expression analysis made easy with DGEasyR](https://github.com/19ADC99/DGEasyR) --> Coming Soon!

**🎲 Other Tools**

- [Low cost flights finder](https://github.com/19ADC99/low-cost-flights) --> Coming Soon!


## 📈 GitHub stats

![](http://github-profile-summary-cards.vercel.app/api/cards/profile-details?username=19ADC99&theme=transparent)
![](http://github-profile-summary-cards.vercel.app/api/cards/stats?username=19ADC99&show_icons=true&theme=transparent)
![](http://github-profile-summary-cards.vercel.app/api/cards/most-commit-language?username=19ADC99&theme=transparent)



## 🧙 "I cast: `'Visitor Number #'`"

![](https://komarev.com/ghpvc/?username=19ADC99&label=Visitor+Number+&0035)



```{r, exec=FALSE, include=FALSE, echo=FALSE}
# links to all badges
# https://gist.github.com/kimjisub/360ea6fc43b82baaf7193175fd12d2f7#file-gistfile1-txt
# <img src="https://img.shields.io/badge/-GitHub Pages-222222?style=flat&logo=githubpages&logoColor=white"/>
```

